The Heavy Photon Search Test Detector

### 2013-10-26 hps-testrun-nim.tex
Adding MCS theory and references. Smaller edits across all sections except ECal and DAQ. [Pelle]

% HPS stuff
%\usepackage{multicol}
\newcommand{\Aprime}{A$^\prime$}
\newcommand{\ee}{e$^+$e$^-$}
\newcommand{\fluenceunit}{1~MeV~neutron~equivalent/cm\ensuremath{^2}}

@@

%% main text
\section{Introduction}
\label{introduction}
One of the more striking anomalies in recent astrophysical observations is an excess of high energy electrons and positrons consistent with a large, unknown source of pair production~\cite{Adriani:2008zr}\cite{FermiLAT:2011ab}. The existence of a massive, hidden sector vector boson; a ``dark photon;" that mixes kinetically with the Standard Model photon and mediates annihilation or decay of dark matter particles is a theoretically attractive explanation of this cosmic-ray excess~\cite{Holdom:1985ag}\cite{ArkaniHamed:2008qn}.
\begin{center}
{\small
\begin{figure*}[ht]
    \includegraphics[width=0.8\textwidth]{figures/hps_testrun_rendering}
\caption{Rendering of the HPS Test apparatus installed on the beam line. SHOULD FIND A PIC WITH LOWER HEIGHT.}
\label{fig:testrundetector}
\end{figure*}
}
\end{center}

@@

The very small signal rate compared to the large background and the need to reconstruct the final states of 
the electron and positron in a dense radiation environment millimeters from a high-current beam 
place stringent requirements on the detector, which should have,
\begin{itemize}
\item large and uniform acceptance in the forward region to catch boosted decay products,
\item a flexible, redundant and efficient trigger selecting electron and positron pairs at rates up to 50kHz,
\item excellent track reconstruction efficiency for electrons and positrons,
\item good angular and momentum resolution to reconstruct invariant mass precisely,
\item excellent vertex resolution to search for displaced heavy photon decays,
\item high rate electronics with event timing resolution down to 2~ns,
\item data acquisition system capable of handling data rates of 100~MB/s to permanent storage,
\item detector components that can survive and efficiently operate in a high radiation environment with 
local doses exceeding $100$~MRad
\end{itemize}

\section{Detector Overview}
\label{detector}
The HPS experiment is proposed to run in Hall B using electron beams of Continuos Electron Beam 
Accelerator Facility (CEBAF) at JLab. CEBAF can simultaneously deliver  electron 
beams to multiple experimental hall at 499 MHz frequency with beam currents of up to 150 $\mu$A (for Hall-B 
the current is limited to $<1 ~\mu$A).  Currently CEBAF facilities are undergoing energy upgrade that will be 
completed in a year. The upgraded CEBAF machine will double its energy range from up to $6$ GeV during 
the HPS test run to $12$ GeV.

The HPS Test apparatus was designed as a 
first step of a multi-stage approach 
to the HPS experiment. The primary goal was to demonstrate that the technology and design approach 
chosen by HPS are sound for running in a challenging environment. Nevertheless, a secondary but 
important aspect was that, after proving the technical concepts,  the apparatus would have the 
capability to discover \Aprime events. The implication was that the design of the HPS Test apparatus 
would be subject to almost the same constraints and requirements as the full experiment.
The kinematics of \Aprime production typically results in final state particles within a few degrees of the incoming beam, especially at low 
$m_{\textrm{A}^\prime}$.  
%Step
This implies that the apparatus for $A^\prime$ search in electron interactions with fix targets must operate in 
close proximity to an intense electron beam that passes through a high-Z target, and 
hence it should tolerate high radiation, high background environment. To meet this challenge, HPS will 
deploy high rate and radiation hard detector composed of 
a silicon vertex tracker with 40 MHz readout and a PbWO$_4$ crystal calorimeter with 250 MHz readout, 
capable of triggering multi-prong events at the rate of up 50 kHz.

@@

The HPS Test apparatus, a simplified version of that 
planned for the full HPS experiment, demonstrates the feasibility of the detector
technologies proposed for the silicon tracker, electromagnetic calorimeter, and data acquisition system. 
A rendering of the HPS Test setup is shown in Fig.~\ref{fig:testrundetector}. The setup is based on the Hall-B 
pair spectrometer (PS) magnet, 18D36 dipole. The silicon tracer was installed inside the vacuum chamber of 
PS, and the electromagnetic calorimeter was mounted behind the vacuum flange. A new vacuum box 
attached to the upstream end of the pair spectrometer vacuum chamber provided necessary connections to 
the tracker (cooling, HV, and signal readout). 
Most technologies used in the HPS Test apparatus as well as the magnet and the vacuum chamber will be 
used in the HPS detector with some 
improvements to each of the systems; both from lessons learned during running of the HPS Test but 
also from planned upgrades for longer and more effective running.

An overview of the coverage, segmentation and performance of the HPS Test detector is given in Tab.~\ref{tab:detector-overview}.

@@

In order to accommodate the dead zone, the SVT and ECal are built in two halves that are mirror reflections of one 
another about the plane of the nominal electron beam.  Each half of SVT consists of five double-sided modules 
mounted on a support plate that provides services to the modules and allows them to be moved as a group 
relative to the dead zone. Each module places a pair of silicon microstrip sensors back-to-back at a 
specified stereo angle with independent cooling and support. The sensors are read out
continuously at 40 MHz using the APV25 chip, developed for the CMS experiment at the
LHC.

The each half of ECal consists of $221$ PbWO$_4$ crystals arranged in rectangular formation, five rows, $46$ modules in each raw with first raw having  $37$ modules. The light readout from each module is performed by Avalanche Photodiode (APD) glued on back surface of the crystal. APD signals were amplified using custom-made amplifier boards before sending them to the readout electronics.

The  Data Acquisition system combines two architectures, Advanced Telecom Communications Architecture (ACTA) based SVT readout system and VXS based digitization and triggering system for ECal. System is designed to run with up to 20 kHz trigger rate.

%\subsection{Electronics, Trigger, Data Acquisition and Online Computing}

@@

%\section{The CEBAF Accelerator and Its Impact on the HPS Test Detector }
%\label{cebaf}
%\subsection{The CEBAF Accelerator}

\section{The HPS Test Beamline}
HPS test run studied multiple Coulomb scattering of electrons and positrons produced in a thin gold foils by 
bremsstrahlung photons from the Hall-B tagged photon facility. In Figure \ref{fig:hpstest_layout}, the layout of 
the test run setup on the beam line is shown. The silicon vertex tracker was installed inside the Hall B pair 
spectrometer magnet vacuum chamber with the electromagnetic calorimeter mounted downstream. Both the 
tracker and the ECal were retracted off the beam plane to allow clean passage of the photon beam through 
the system. 
\begin{figure}[ht]
    \includegraphics[width=0.5\textwidth]{figures/HPS_dimensions}
\caption{\small{Layout of the HPS parasitic run.} }
\label{fig:hpstest_layout}
\end{figure}

The photon beam was generated in the interaction of the $5.5$ GeV electrons with a gold radiator of 
$10^{-4}$ r.l., located $\approx 8$ meters upstream of the PS pair converter. The primary and scattered 
electron beams are deflected way from detectors by the dipole magnet of the photon tagging system. After 
collimation ($D=6.4$ mm), the photon beam passes through the pair converter and through the HPS system. 
The converter was located $\approx 77$~cm upstream of the first layer of the silicon vertex tracker. Data were 
taken on different converters (empty, $1.8\times 10^{-3}$ r.l., $4.5\times 10^{-3}$ r.l., and $1.6\times 10^{-2}$ 
r.l.). These measurements were repeated for the reverse field setting of the pair spectrometer dipole.

@@

The principle purpose of the HPS Test Silicon Vertex Tracker (SVT) is the efficient detection of 
charged particles and reconstruction of their momentum and angles. The precise measurements 
forms the primary input to the extraction of a signal from \Aprime decays; both from the precise 
measurement of the invariant mass of it's \ee decay products and the position of it's decay vertex 
downstream of the target. Track reconstruction is also important for energy scale calibration of the 
electromagnetic calorimeter due to the better momentum resolution of tracks compared to clusters 
in the calorimeter.

@@

The design of the SVT presents a number of significant challenges.  First, the A$^\prime$ decay products 
have momenta in the range of 1 GeV, so multiple scattering dominates mass and vertexing errors for any 
possible material budget.  Therefore, the construction of the SVT must place the smallest amount of 
material in the tracking volume.  Second, the signal yield for long-lived A$^\prime$ will be very small, so 
the rejection of prompt vertexes must be exceedingly pure, on the order of $10^{-7}$, in order to eliminate 
all prompt backgrounds.  This requires great care in design, calibration, and operation of the detector. 
Finally, the passage of degraded primary beam through the apparatus creates a region of extreme 
occupancy and radiation that is critical for sensitivity to low-mass A$^\prime$ that have decay products 
nearly collinear with the beam.  This places low-mass acceptance in opposition to tracking and vertexing 
purity and the longevity of the detector.

It is this last challenge that has the most interesting and obvious impacts on the design of the SVT. To 
achieve good vertexing performance, the first layer must be placed no more than about 10 cm downstream 
of the target. At that distance, it is found that the active region of a sensor can be placed as close to 1.5 mm 
from the center of the beam, defining a 15 mrad ``dead zone" in the detector around the plane of the 
primary beam. At the edge of this ``dead zone," the radiation dose approaches $10^{15}$ electrons/cm
$^2$/month, or roughly $3 \times 10^{14}$~\fluenceunit/month, as shown in Fig.~
\ref{fig:radiation} 
%===================
\begin{figure}[]
\includegraphics[width=7cm]{figures/radiation}
\label{fig:radiation}
\caption{Simulation of the fluence 10~cm downstream of the target in the active region of the SVT ($|Y|>0.15~$cm) looking downstream; electrons bend towards $+x$.}
\end{figure}
%===================
and~\ref{fig:rates}~\cite{Rashevskaya:2002nd}.
%===================
\begin{figure}[]
\includegraphics[width=7cm]{figures/rates}
\label{fig:rates}
\caption{Simulation of the occupancy in the SVT 10~cm downstream of the target as a function of the 
vertical distance from the beam center.}
\end{figure}
%=================== 
This requires the sensors to be actively cooled. Meanwhile, very low-energy delta rays from beam gas interactions multiply the density of background hits, so the SVT must operate inside the beam vacuum.  Finally, in order protect the sensors, the detector must be movable so that it can be retracted during periods of uncertain beam conditions.  
%To summarize the SVT must:
%\begin{itemize}
%\item have a uniform acceptance in the forward region; up to $\theta_y=XXXXmrad$ and as close as 
%possible to the beam axis to catch boosted decay products,
%\item >95\% reconstruction efficiency for electron and positrons  with energy down to $XXXX$~MeV,
%\item momentum resolution of XXXX\% to separate a promptly decaying \Aprime signal from the irreducible background,
%\item vertex resolution $<XXXX$~mm along the beam line direction to search for displaced \Aprime decays,
%\item event timing resolution down to 2~ns, 
%\item sustain a occupancy of up to 1\%, trigger rates of $\approx50$~kHz and data rates up to 100~MB/s,
%\item survive and efficiently operate after $1\times10^{14} neutron eq. fluence,
%
%dosedetector components that can survive and efficiently operate in a high radiation environment with 
%local doses exceeding $XXXX$~MRad
%\end{itemize}

@@

A realistic {\sc Geant4} simulation of the detector based on the {\sc SLIC} simulation 
package~\cite{Graf:2011zzc}
including all backgrounds has been used to optimize the layout for acceptance, tracking efficiency, mass 
resolution and prompt vertex rejection. The layout of the SVT is summarized in Tab.~\ref{tab:trk} and rendered in Fig.~\ref{fig:tracker_model}.

The layout of the SVT is shown in Fig.~\ref{fig:tracker_model} and summarized in Table \ref{tab:trk}.
The vertex resolution with an asymmetric beam spot of $\approx 200\times40 \mu$m requires hit 
resolutions better than XXXX (XXXX)~$\mu$m in the vertical (horizontal) measurement coordinate. 
In addition, the vacuum chamber is too small vertically to accommodate 90-degree stereo layers to optimize 
the vertex resolution in the horizontal coordinate. Instead, 100~mrad stereo is used in the first three layers 
to provide higher-resolution 3-D space points for vertexing. The 50~mrad stereo of the last two layers 
breaks the tracking degeneracy of having five identical layers and minimizes fakes from ghost hits, 
improving pattern recognition while still providing sufficient pointing resolution into the third layer
 for robust hit 
association in the denser environment there. Altogether, this layout comprises 20 sensors and hybrids and 
100 APV25 chips for a total of 12780 readout channels. 
%=======================
\begin{center}
\begin{table}[ht]
{\small
\begin{tabular}{lccccc}   
\hline \hline 
    Layer & 1 & 2 & 3 & 4 & 5 \\      
\hline
    $z$ from nom. target (cm)  & 10 & 20 & 30 & 50 & 70  \\ 
    Stereo angle (mrad)  & 100 & 100 & 100 & 50 & 50 \\ 
    Bend res. ($\mu$m)  & $\approx$60 & $\approx$60 & $\approx$60 & $\approx$120 & $\approx$120  \\ 
    Non-bend res. ($\mu$m)  & $\approx$6 & $\approx$6 & $\approx$6 & $\approx$6 & $\approx$6  \\ 
    \# of sensors  & 4 & 4 & 4 & 4 & 4  \\ 
    Dead zone (mm) & $\pm1.5$  & $\pm3.0$  & $\pm4.5$  & $\pm7.5$  & $\pm10.5$  \\ 
    Power cons. (W) & 6.9 & 6.9 & 6.9 & 6.9 & 6.9 \\
\hline \hline
\end{tabular}
\caption{Layout of the HPS Test SVT.  Note the elimination of one layer and 90-degree stereo, and the use of only small, single-sensor-sized double-sided modules both above and below he dead zone. }
}
\label{tab:trk} 
\end{table}
\end{center}
%=======================
\begin{center}
\begin{figure}[htp]
    \includegraphics[width=7cm]{figures/HPS_nochamber}
\caption{A rendering of the Test SVT showing the modules on their support plates held by the hinged C-support on the left and the motion levers on the right. The sensors are shown in red and the hybrids in green. The beam enters from the right through a vacuum box with flanges for services. }
\label{fig:tracker_model}
\vspace*{-5mm}
\end{figure}
\end{center}
%=======================
The SVT is built in two separate halves that are mirror reflections of one another about the plane of the 
nominal electron beam.  Each half consists of five, double-sided modules mounted on a support plate that 
provides services to the modules and allows them to be moved as a group relative to the dead zone. The 
two halves of the tracker are connected to hinges mounted on a C-shaped support just beyond layer 5 that 
defines the nominal spacing between the upper and lower halves of the tracker.  A shaft attached to each 
support plate in front of layer 1 extends upstream and connects to a linear shift that transfers motion into the 
vacuum box through bellows to open and close the tracker around the dead zone. The C-support is 
mounted to an aluminum baseplate that defines the position of the SVT with respect to the vacuum 
chamber. Figure~\ref{fig:tracker_halves} shows a photograph of both completed detector halves prior to 
final assembly. 
%=======================
\begin{figure}[htp]
\begin{center}
    \includegraphics[width=7cm]{figures/2012-101-PHOTON-DETECTOR-001}
\caption{\small{Both halves of the HPS Test SVT after final assembly at SLAC.  The cooling manifolds and 
integrated cable runs are clearly seen.} }
\label{fig:tracker_halves}
\end{center}
\vspace*{-5mm}
\end{figure}
%=======================

@@

\subsubsection{Silicon Sensors}
The sensors for the SVT are selected according to a number of requirements.  First, the sensors must be 
radiation tolerant to approximately $1.5\times10^{14}$~\fluenceunit for a six month run.  This 
corresponds to about 4~MHz/mm$^2$, so the sensor and readout technology must be capable of handling 
very high local occupancies. Since sensitivity is limited by multiple scattering, a material budget of less 
than 1\% $X_0$/layer is imperative and far less is desirable. To achieve the required vertex resolution  
single-hit resolutions better than XXXX~$\mu$m are required. Finally, the sensor technology must 
be mature and readily available at low cost.  Silicon microstrips are the best match to these requirements, and 
a supply of appropriate microstrip sensors purchased from the Hamamatsu Photonics Corporation for the 
Run 2b upgrade of D\O~\cite{Denisov:2001aa} are readily available. 
These are $p+$-on-$n$, single sided, AC coupled, 
polysilicon-biased sensors fabricated on $<100>$ silicon and have 30(60) micron sense(readout) pitch 
over their 4 cm 
$\times$ 10 cm surface. Although a maximum bias of 350 V is specified, the vast majority are operable to 
1000V and therefore remain fully depleted to a dose of approximately 
$1.5\times10^{14}$~\fluenceunit.

\subsubsection{Front-end Electronics}
Because the regions of high occupancy are small spots in two dimensions, only a short length of any one 
strip sees significant occupancy, and the strips in that region act as long pixels. However, the rates are still 
very high and lowering the peak occupancy in the sensors to approximately 1\% for tracking requires a 
trigger window and tagging of hit times to roughly 8~ns, as shown in Fig.~\ref{fig:rates}.  The FADC 
readout for the ECal and muon system are capable of this, but achieving achieving $2\sigma$ efficiency for 
silicon hits then requires 2~ns time resolution for the hits in the SVT. This performance can be achieved with 
the APV25 readout ASIC developed for the CMS experiment at CERN~\cite{French:2001xb}.  When 
operated in ``multi-peak mode", the APV25 captures successive samples of the output of the shaper in sets 
of three.  By fitting the known $CR$-$RC$ shaping curve to these samples, the initial time of the hit can be 
determined to a precision of 2~ns for S/N$>25$, an achievable figure with our sensors if read out 
individually~\cite{Friedl:2009zz}.  For the SVT, six-sample readout and the shortest possible shaping time 
(35~ns) will be used to best distinguish hits that overlap in time.
The APV25 chips are hosted on simple FR4 hybrids since these hybrids and their cooling system are 
outside the tracking volume.  Along with the sensors, these are assembled into half-modules, one for each 
tracking view, with a short cable pigtail to provide power and configuration to the modules and signal 
readout.

@@

\section{Summary and Outlook}

>>>>

% HPS stuff
\usepackage{color}
%\usepackage{multicol}
\newcommand{\Aprime}{A\ensuremath{^\prime}}
\newcommand{\ee}{e$^+$e$^-$}
\newcommand{\fluenceunit}{1~MeV~neutron~equivalent/cm\ensuremath{^2}}
\newcommand{\geant}{{\sc Geant4}}
\newcommand{\egs}{{\sc EGS5}}
\newcommand{\moliere}{Moli\`{e}re}

@@

%% main text
\section{Introduction}
\label{introduction}
One of the more striking anomalies in recent astrophysical observations is an excess of high energy electrons and positrons consistent with a large, unknown source of pair production~\cite{Adriani:2008zr}\cite{FermiLAT:2011ab}. The existence of a massive, hidden sector vector boson; a ``dark photon;" that mixes kinetically with the Standard Model photon and mediates annihilation or decay of dark matter particles is a theoretically attractive explanation of this cosmic-ray excess~\cite{Holdom:1985ag}\cite{ArkaniHamed:2008qn}.
\begin{center}
{\small
\begin{figure*}[ht]
    \includegraphics[width=0.8\textwidth]{figures/hps_testrun_rendering}
\caption{Rendering of the HPS Test apparatus installed on the beam line.}
\label{fig:testrundetector}
\end{figure*}
}
\end{center}

@@

The very small signal rate compared to the large background and the need to reconstruct the final states of 
the electron and positron in a dense radiation environment millimeters from a high-current beam 
place stringent requirements on the detector, which should have,
\begin{itemize}
\item large and uniform acceptance in the forward region to catch boosted decay products,
\item a flexible, redundant and efficient trigger selecting electron and positron pairs at rates up to 50kHz,
\item excellent track reconstruction efficiency for electrons and positrons,
\item good angular and momentum resolution to reconstruct invariant mass precisely,
\item excellent vertex resolution to search for displaced heavy photon decays,
\item high rate electronics with event timing resolution down to 2~ns,
\item data acquisition system capable of handling data rates of 100~MB/s to permanent storage,
\item detector components that can survive and efficiently operate in a high radiation environment with 
local doses exceeding $100$~Mrad
\end{itemize}

\section{Detector Overview}
\label{detector}
The HPS experiment is proposed to run in Hall B using electron beams of Continuos Electron Beam 
Accelerator Facility (CEBAF) at JLab. CEBAF can simultaneously deliver  electron 
beams to multiple experimental hall at 499 MHz frequency with beam currents of up to 150 $\mu$A (Hall-B 
is limited to $<1 ~\mu$A).  Currently CEBAF facilities are undergoing energy an upgrade that is expected to be 
completed in end of 2014. The upgraded CEBAF machine will double its maximum energy from $6$~GeV 
during the HPS test run to $12$~GeV.

The HPS Test apparatus was designed as a 
first step of a multi-stage approach 
to the HPS experiment. The primary goal was to demonstrate that the technology and design approach 
chosen are sound for running in such a challenging environment. Nevertheless, a secondary but 
important aspect was that, after proving the technical concepts,  the apparatus would have the 
capability to discover \Aprime events. The implication was that the design of the HPS Test apparatus 
would be subject to almost the same constraints and requirements as the full experiment.
The kinematics of \Aprime production typically results in final state particles within a few degrees of the incoming beam, especially at low 
$m_{\Aprime}$.  
%Step
This implies that the apparatus for an \Aprime search in electron interactions with fix targets must operate in 
close proximity to an intense electron beam that passes through a high-Z target. 
Hence it should cope with high backgrounds and tolerate the high radiation environment. 
To meet this challenge, HPS will deploy high rate and radiation hard detector composed of 
a silicon vertex tracker with 40~MHz readout and a PbWO$_4$ crystal calorimeter with 250~MHz 
readout, capable of triggering multi-prong events at top to 50~kHz rate.

@@

The HPS Test apparatus, a simplified version of that 
planned for the full HPS experiment, demonstrates the feasibility of the detector
technologies proposed for the silicon tracker, electromagnetic calorimeter, and data acquisition system. 
A rendering of the HPS Test setup is shown in Fig.~\ref{fig:testrundetector}. The setup is based on the Hall-B 
pair spectrometer (PS) magnet, 18D36 dipole. The silicon vertex tracker (SVT) was installed inside the vacuum 
chamber of PS and the electromagnetic calorimeter (ECal) was mounted behind the vacuum flange. 
A new vacuum box 
attached to the upstream end of the pair spectrometer vacuum chamber provided necessary services to 
the SVT (cooling, power and signal readout). 
Most technologies used in the HPS Test apparatus as well as the magnet and the vacuum chamber will be 
used in the HPS detector with some 
improvements to each of the systems; both from lessons learned during running of the HPS Test but 
also from planned upgrades for longer and more effective running.

@@

An overview of the coverage, segmentation and performance of the HPS Test detector is given in 
Tab.~\ref{tab:detector-overview}.  In order to accommodate the dead zone, the SVT and ECal are built in two 
halves that are mirror reflections of one 
another about the plane of the nominal electron beam.  Each half of the SVT consists of five double-sided 
modules 
mounted on a support plate that provides services to the modules and allows them to be moved as a group 
relative to the dead zone. Each module places a pair of silicon microstrip sensors back-to-back at a 
specified stereo angle with independent cooling and support. The sensors are read out
continuously at 40~MHz using the APV25 ASIC, developed for the CMS experiment at the
LHC.

Each half of the ECal consists of 221 PbWO$_4$ crystals arranged in rectangular formation. 
There are five rows with 46 
modules in each row except the row closest to the beam plane which has 37. The light from each crystal is read 
out by Avalanche Photodiode (APD) glued on the back surface of the crystal. 
Signals from the APDs were amplified using custom-made amplifier boards before being sent to the readout 
electronics.

The  Data Acquisition system combines two architectures, the Advanced Telecom Communications 
Architecture (ATCA) based SVT readout system and VXS based digitization and triggering system for the ECal. 
The system was designed to run at up to a 20 kHz trigger rate.

@@

\section{The HPS Test Beamline}
The HPS Test run studied multiple Coulomb scattering of electrons and positrons from bremsstrahlung photons 
produced in the Hall-B tagged photon facility. Figure~\ref{fig:hpstest_layout} shows the layout of 
the HPS Test setup on the beam line. The SVT was installed inside the Hall B pair 
spectrometer magnet (PS) vacuum chamber with the ECal mounted downstream of it. Both the 
SVT and the ECal were retracted off the beam plane to allow clean passage of the photon beam through 
the system. 
\begin{figure}[ht]
    \includegraphics[width=0.5\textwidth]{figures/HPS_dimensions}
\caption{\small{Layout of the HPS parasitic run.} }
\label{fig:hpstest_layout}
\end{figure}

The photon beam was generated in the interaction of the $5.5$ GeV electrons with a gold radiator of 
$10^{-4}~X_0$, located $\approx~9$~m upstream of the PS. The primary beam and scattered 
electrons are deflected away from detectors by the dipole magnet of the photon tagging system. After 
collimation (6.4~mm diameter), the photon beam passes through the aluminum PS pair converter and 
later the HPS system. 
The converter was located $\approx~77$~cm upstream of the first layer of the silicon vertex tracker. Data was 
taken on different converters (empty, $1.8\times 10^{-3}~X_0$ , $4.5\times 10^{-3}~X_0$ and 
$1.6 \times 10^{-2}~X_0$). 
These measurements were repeated with the reverse field setting of the PS dipole magnet.

@@

The principle purpose of the HPS Test Silicon Vertex Tracker (SVT) is the efficient detection of 
charged particles and reconstruction of their momentum and angles. The precise measurements 
forms the primary input to the extraction of a signal from \Aprime decays; both from the precise 
measurement of the invariant mass of its \ee decay products and the position of its decay vertex 
downstream of the target. Track reconstruction is also important for energy scale calibration of the 
electromagnetic calorimeter due to the better momentum resolution of tracks compared to clusters 
in the calorimeter.

@@

The design of the SVT presents a number of significant challenges.  First, the A$^\prime$ decay products 
have momenta in the range of 1 GeV, so multiple scattering dominates mass and vertexing errors for any 
possible material budget.  Therefore, the construction of the SVT must place the smallest amount of 
material in the tracking volume.  Second, the signal yield for long-lived A$^\prime$ will be very small, so 
the rejection of prompt vertexes must be exceedingly pure, on the order of $10^{-7}$, in order to eliminate 
all prompt backgrounds.  This requires great care in design, calibration, and operation of the detector. 
Finally, the passage of the degraded primary beam through the apparatus creates a region of extreme 
occupancy and radiation that is critical for sensitivity to low-mass A$^\prime$ that have decay products 
nearly collinear with the beam.  This places low-mass acceptance in opposition to tracking and vertexing 
purity and the longevity of the detector.

It is this last challenge that has the most interesting and obvious impacts on the design of the SVT. To 
achieve good vertexing performance, the first layer must be placed no more than about 10 cm downstream 
of the target. At that distance, it is found that the active region of a sensor can be placed as close to 1.5 mm 
from the center of the beam, defining a 15 mrad ``dead zone" in the detector around the plane of the 
primary beam. At the edge of this ``dead zone," the radiation dose approaches $10^{15}$ electrons/cm
$^2$/month, or roughly $3 \times 10^{14}$~\fluenceunit/month~\cite{Rashevskaya:2002nd}, as shown in 
Fig.~\ref{fig:radiation} and~\ref{fig:rates}.
%===================
\begin{figure}[]
\includegraphics[width=7cm]{figures/radiation}
\label{fig:radiation}
\caption{\small Simulation of the fluence 10~cm downstream of the target in the active region of the SVT ($|Y|>0.15~$cm) looking downstream; electrons bend towards $+x$.}
\end{figure}
%===================
%===================
\begin{figure}[]
\includegraphics[width=7cm]{figures/rates}
\label{fig:rates}
\caption{\small Simulation of the occupancy in the SVT 10~cm downstream of the target as a function of the 
vertical distance from the beam center.}
\end{figure}
%=================== 
This requires the sensors to be actively cooled. Meanwhile, very low-energy delta rays from beam gas interactions multiply the density of background hits, so the SVT must operate inside the beam vacuum.  Finally, in order to protect the sensors, the detector must be movable so that it can be retracted during periods of uncertain beam conditions.  
%To summarize the SVT must:
%\begin{itemize}
%\item have a uniform acceptance in the forward region; up to $\theta_y=XXXXmrad$ and as close as 
%possible to the beam axis to catch boosted decay products,
%\item >95\% reconstruction efficiency for electron and positrons  with energy down to $XXXX$~MeV,
%\item momentum resolution of XXXX\% to separate a promptly decaying \Aprime signal from the irreducible background,
%\item vertex resolution $<XXXX$~mm along the beam line direction to search for displaced \Aprime decays,
%\item event timing resolution down to 2~ns, 
%\item sustain a occupancy of up to 1\%, trigger rates of $\approx50$~kHz and data rates up to 100~MB/s,
%\item survive and efficiently operate after $1\times10^{14} neutron eq. fluence,
%
%dosedetector components that can survive and efficiently operate in a high radiation environment with 
%local doses exceeding $XXXX$~MRad
%\end{itemize}

@@

A realistic \geant~\cite{Agostinelli2003250} simulation of the detector based on the {\sc SLIC} simulation 
package~\cite{Graf:2011zzc}
including all backgrounds has been used to optimize the layout for acceptance, tracking efficiency, mass 
resolution and prompt vertex rejection. The layout of the SVT is summarized in Tab.~\ref{tab:trk} and rendered in Fig.~\ref{fig:tracker_model}.

The vertex resolution with an asymmetric beam spot of $\approx200\times40~\mu$m requires hit 
resolutions better than XXXX (XXXX)~$\mu$m in the vertical (horizontal) measurement coordinate. 
In addition, the vacuum chamber is too small vertically to accommodate 90-degree stereo layers to optimize 
the vertex resolution in the horizontal coordinate. Instead, 100~mrad stereo is used in the first three layers 
to provide higher-resolution 3D space points for vertexing. The 50~mrad stereo of the last two layers 
breaks the tracking degeneracy of having five identical layers and minimizes fakes from ghost hits, 
improving pattern recognition while still providing sufficient pointing resolution into the third layer
 for robust hit 
association in the denser environment there. Altogether, this layout comprises 20 sensors and hybrids and 
100 APV25 chips for a total of 12780 readout channels. 
%=======================
\begin{center}
\begin{table}[ht]
{\small
\begin{tabular}{lccccc}   
\hline \hline 
    Layer & 1 & 2 & 3 & 4 & 5 \\      
\hline
    $z$ from nom. target (cm)  & 10 & 20 & 30 & 50 & 70  \\ 
    Stereo angle (mrad)  & 100 & 100 & 100 & 50 & 50 \\ 
    Bend res. ($\mu$m)  & $\approx$60 & $\approx$60 & $\approx$60 & $\approx$120 & $\approx$120  \\ 
    Non-bend res. ($\mu$m)  & $\approx$6 & $\approx$6 & $\approx$6 & $\approx$6 & $\approx$6  \\ 
    \# of sensors  & 4 & 4 & 4 & 4 & 4  \\ 
    Dead zone (mm) & $\pm1.5$  & $\pm3.0$  & $\pm4.5$  & $\pm7.5$  & $\pm10.5$  \\ 
    Power cons. (W) & 6.9 & 6.9 & 6.9 & 6.9 & 6.9 \\
\hline \hline
\end{tabular}
\caption{\small Layout of the HPS Test SVT.. }
}
\label{tab:trk} 
\end{table}
\end{center}
%=======================
\begin{center}
\begin{figure}[htp]
    \includegraphics[width=7cm]{figures/HPS_nochamber}
\caption{\small A rendering of the HPS Test SVT showing the modules on their support plates held by the 
hinged C-support on the left and the motion levers on the right. The sensors are shown in red and the hybrid 
readout boards in green. The beam enters from the right through a vacuum box with flanges for services. }
\label{fig:tracker_model}
\vspace*{-5mm}
\end{figure}
\end{center}
%=======================
The SVT is built in two separate halves that are mirror reflections of one another about the plane of the 
nominal electron beam.  Each half consists of five, double-sided modules mounted on a support plate that 
provides services to the modules and allows them to be moved as a group relative to the dead zone. The 
two halves of the tracker are connected to hinges mounted on a C-shaped support just beyond the last layer t
that defines the nominal spacing between the upper and lower halves of the tracker.  A shaft attached to each 
support plate in front of layer 1 extends upstream and connects to a linear shift that transfers motion into the 
vacuum box through bellows to open and close the two halves around the dead zone. The C-support is 
mounted to an aluminum baseplate that defines the position of the SVT with respect to the vacuum 
chamber. Figure~\ref{fig:tracker_halves} shows a photograph of both completed detector halves prior to 
final assembly. 
%=======================
\begin{figure}[htp]
\begin{center}
    \includegraphics[width=7cm]{figures/2012-101-PHOTON-DETECTOR-001}
\caption{\small{Both halves of the HPS Test SVT after final assembly at SLAC.  The cooling manifolds and 
integrated cable runs are clearly seen.} }
\label{fig:tracker_halves}
\end{center}
\vspace*{-5mm}
\end{figure}
%=======================

@@

\subsubsection{Silicon Sensors}
The sensors for the SVT are selected according to a number of requirements.  First, the sensors must be 
radiation tolerant to approximately $1.5\times10^{14}$~\fluenceunit for a six month run.  This 
corresponds to about 4~MHz/mm$^2$, so the sensor and readout technology must be capable of handling 
very high local occupancies. Since sensitivity is limited by multiple scattering, a material budget of less 
than 1\% $X_0$/layer is imperative and far less is desirable. To achieve the required vertex resolution  
single-hit resolutions better than XXXX~$\mu$m are required. Finally, the sensor technology must 
be mature and readily available at low cost.  Silicon microstrips are the best match to these requirements, and 
a supply of appropriate microstrip sensors purchased from the Hamamatsu Photonics Corporation for the 
Run 2b upgrade of the D\O experiment~\cite{Denisov:2001aa} are readily available. 
These are $p+$-on-$n$, single sided, AC coupled, 
polysilicon-biased sensors fabricated on $<100>$ silicon and have 30 (60) micron sense (readout) pitch 
over their $4\times10$~cm$^2$ surface. Although a maximum bias of 350~V is specified, the vast majority are 
operable to 1000~V and therefore remain fully depleted to a dose of approximately 
$1.5\times10^{14}$~\fluenceunit.

\subsubsection{Front-end Electronics}
Because the regions of high occupancy are small spots in two dimensions, only a short length of any one 
strip see a significant occupancy, and the strips in that region act as long pixels. However, the rates are still 
very high and lowering the peak occupancy in the sensors to approximately 1\% for tracking requires a 
trigger window and tagging of hit times to roughly 8~ns, as shown in Fig.~\ref{fig:rates}.  The FADC 
readout for the ECal and muon system are capable of this (see Sec.~\ref{sec:fadc}), but achieving 
$2\sigma$ efficiency for 
silicon hits then requires 2~ns time resolution for the hits in the SVT. This performance can be achieved with 
the APV25 readout ASIC developed for the CMS experiment at CERN~\cite{French:2001xb}.  When 
operated in ``multi-peak mode", the APV25 captures successive samples of the output of the shaper in sets 
of three at a sampling rate of approximately 40~MHz.  
By fitting the known $CR$-$RC$ shaping curve to these samples, the initial time of the hit can be 
determined to a precision of 2~ns for S/N$>25$, an achievable figure with our sensors if read out 
individually~\cite{Friedl:2009zz}.  For the SVT, six-sample readout and the shortest possible shaping time 
(35~ns) will be used to best distinguish hits that overlap in time.
The APV25 ASICs are hosted on simple FR4 hybrids since these hybrids and their cooling system are 
outside the tracking volume.  Along with the sensors, these are assembled into half-modules, one for each 
tracking view, with a short cable pigtail to provide power and configuration to the modules and signal 
readout.

@@

\section{Summary}
